---
title: "Empirical Analyses"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(MASS)
library(ggridges)
```

# read in data

```{r, echo= TRUE, message=FALSE, warning=FALSE}

florida_8_3 <- read.csv("~/Documents/work/Spacial_adj/Data_and_Figures/Florida_fixed_8_3_2014dm2.csv", header = TRUE)
florida_8_5 <- read.csv("~/Documents/work/Spacial_adj/Data_and_Figures/Florida_fixed_8_5_2014dm2.csv", header = TRUE)
  
oregon_6_2 <- read.csv("~/Documents/work/Spacial_adj/Data_and_Figures/Oregon_fixed__6_2_2014dm2.csv", header = TRUE)
oregon_7_1 <-  read.csv("~/Documents/work/Spacial_adj/Data_and_Figures/Oregon_fixed__7_1_2014dm2.csv", header = TRUE)
```

# Upper + lower interior/ total ratio Helper functions

These functions provide the bounds on upper and lower interior / total ratios for different numbers of pixels. 

```{r, echo=TRUE, message=FALSE, warning=FALSE}

upper_bound_ratios <- function(x){
  upper <- rep(NA, length(x))
  edge <- rep(NA, length(x))
  interior <- rep(NA, length(x))
  
  ## get edges
  for(i in seq_along(x)){
    smaller_sqrt <- floor(sqrt(x[i]))
    smaller_square <- smaller_sqrt^2
    
    larger_sqrt <- ceiling(sqrt(x[i]))
    
    remainder <- x[i] %% smaller_square
    
    if (remainder > smaller_sqrt){
      edge[i] <- 4 * larger_sqrt
    }
    
    if (remainder <= smaller_sqrt){
      edge[i] <- (2*smaller_sqrt) + 2*(1+smaller_sqrt)
    }
    
    if (remainder == 0){
      edge[i] <- 4 * larger_sqrt
    }
  }
  
  #get interiors
  for (i in seq_along(x)){
    interior[i] <- 4 * x[i]
    interior[i] <- interior[i] - edge[i]
  }
  
  for (i in seq_along(x)){
    if (x[i] == 1){
      upper[i] <- 0
      next  
    }
    if (x[i] == 2){
      upper[i] <- 0.25
      next
    }
    if (x[i] == 3){
      upper[i] <- 0.5
      next 
    }
    
    upper[i] <- interior[i] / (interior[i] + edge[i])
  }
  
  
  return(upper)
}

lower_bound_ratios <- function(x){
  lower <- rep(NA, length(x))
  edge <- rep(NA, length(x))
  interior <- rep(NA, length(x))
  
  for (i in seq_along(x)){
    if(x[i] == 1){
      edge[i] <- 4
      next
    }
    
    if (x[i] == 2){
      edge[i] <- 6  
      next
    }
    
      edge[i] <- (2 * (x[i] - 2)) + 6 # The six accounts for sides of the two end pixels 
  }
  
  for (i in seq_along(x)){
    if(x[i] == 1){
    interior[i] <- 0
     lower[i] <- interior[i] / (interior[i] + edge[i])
      next
    }
    
    if (x[i] == 2){
     interior[i] <- 2
      lower[i] <- interior[i] / (interior[i] + edge[i])
      next
    }
    
     interior[i] <- ((4 * x[i]) - edge[i])
     lower[i] <- interior[i] / (interior[i] + edge[i])
  }
  return (lower)
}


```

# Sifting out edge-cases with artificial ratio inflation

The base raster adjacency function that we used when calculating interior/total ratios made a wrap-around adjacency assumption, inflating the adjacency of corner and edge pixels. We corrected for it by setting ratios above the maximum to NA. 

In addition, the LANDFIRE dataset had two seperate catagories for "Unknown". They are: "Unknown/Fire Doubtful" - a catagory that replaced the initial 2000 "Unknown" catagory, and "Unknown/Possibly Fire". For our analysis, both catagories were considered "Unknown". 

```{r, echo=TRUE, message=FALSE, warning=FALSE}
oregon_6_2$eco_II <- "6.2"  ## Put in Ecoregion labels 
oregon_7_1$eco_II <- "7.1"
florida_8_3$eco_II <- "8.3"
florida_8_5$eco_II <- "8.5"

florida <- rbind(florida_8_3, florida_8_5) 
oregon <- rbind(oregon_6_2, oregon_7_1)

florida$size_ha <- florida$sizw * 0.09  ## Convert Pixels to ha
oregon$size_ha <- oregon$sizw * 0.09

florida$state <- "FL"  ## State Labels 
oregon$state <- "OR"
final <- rbind(florida, oregon)

## Correcting for wrap-around ratio inflation
final$ratio[(final$ratio > 0.25) & (final$sizw == 2)] <- NA
final$ratio[(final$ratio > 0.33) & (final$sizw == 3)] <- NA
final$ratio[(final$ratio > 0.50) & (final$sizw == 4)] <- NA
final$ratio[(final$ratio > 0.5 ) & (final$sizw == 5)] <- NA
final$ratio[(final$ratio > 0.55333333) & (final$sizw == 6)] <- NA
final$ratio[(final$ratio > 0.5714286) & (final$sizw == 7)] <- NA
final$ratio[(final$ratio >  0.7083333) & (final$sizw == 12)] <- NA
final$ratio[(final$ratio >  0.7631579) & (final$sizw == 19)] <- NA

## 2014 specific ID's
#final[final$ids == 212, ]$dist_name <- "Wildfire"
  final[final$ids == 231, ]$dist_name <- "Wildfire"
  
## Check that all remaining unnamed ID's are in 1100's range  
ids_of_unnamed <- unique(final[final$dist_name == "",]$ids)
tmp <- strsplit(as.character(ids_of_unnamed), split="\\s+")
tmp <- unlist(tmp)
tmp <- as.numeric(tmp)
all_unknowns <- all(tmp > 1100)

if (all_unknowns){
  final[final$dist_name == "",]$dist_name <- "Unknown"
}else{
  print("NOT ALL UNKNOWNS, RECHECK PARSING")
}

## New Column that treats mixed disturbance as a type of disturbance
final$dist_name2 <- final$dist_name
final <- as.data.frame(final, stringsAsFactors = FALSE)
final$dist_name2 <- as.character(final$dist_name2)
final[grep(",", final$dist_name),]$dist_name2 <- "Mixed"

```


## Analyses & Descriptive statistics

# Subset Dataset for percentenge estimates of mixed disturbence types, and unknowns

```{r, echo=TRUE, message=FALSE, warning=FALSE}

unknowns <- final[grep("Unknown", final$dist_name) ,]   
no_unknowns <- dplyr::anti_join(final, unknowns, by = "dist_name") 
mixed_disturbence <- final[grep(",", final$dist_name), ]
single_disturbence <- dplyr::anti_join(final, mixed_disturbence, by = "dist_name")

single_disturbence <- na.omit(single_disturbence)

no_unknowns_mixed_disturbence <- dplyr::anti_join(mixed_disturbence, unknowns, by = "dist_name") 
no_unknowns_single_disturbence <- dplyr::anti_join(single_disturbence, unknowns, by = "dist_name")
unknown_only <- dplyr::anti_join(unknowns, mixed_disturbence, by = "dist_name")

```

```{r}
dist_8_3 <- unique(single_disturbence[single_disturbence$eco_II == 8.3,]$dist_name)
dist_8_5 <- unique(single_disturbence[single_disturbence$eco_II == 8.5,]$dist_name)
dist_7_1 <- unique(single_disturbence[single_disturbence$eco_II == 7.1,]$dist_name)
dist_6_2 <- unique(single_disturbence[single_disturbence$eco_II == 6.2,]$dist_name)

common_disturbences <- Reduce(intersect, list(dist_8_3,dist_8_5,dist_7_1, dist_6_2))
common_disturbences <- common_disturbences[common_disturbences != ""]

disturbences_names <-  common_disturbences # These are the disturbences that are common between 4 ecoregions
all_disturbences <-  unique(final$dist_name2)
all_disturbences <- all_disturbences[all_disturbences != "Disease" & all_disturbences != "Biological"]
## 

## Create usefull conditional for plotting just common disturbances
null_model_conditional <- single_disturbence$sizw >3 & single_disturbence$dist_name %in% disturbences_names 

## Set up common color schemes 
disturbence_colors <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f')   #,'#ff7f00','#cab2d6')

disturbence_colors_all <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f'   ,'#ff7f00','#cab2d6', '#6a3d9a', '#ffff99', '#b15928')#, '#01665e' ), '#bababa')

eco_region_colors <- c('#df65b0', '#67001f', '#081d58','#7fcdbb') # Oregon then Florida

state_colors <- c('#980043', "#225ea8")

## Tie colors to disturbance types
color_cheat_sheet <- cbind(disturbence_colors_all, sort(all_disturbences))
color_cheat_sheet <- as_data_frame(color_cheat_sheet)
colnames(color_cheat_sheet) <- c("colors", "dist")
color_cheat_sheet$all_eco <- color_cheat_sheet$dist %in% disturbences_names

```



# Estimate qa/qc stats for supplemental table 1

```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(lemon)
library(knitr)

## Estimate unknown disturbence in an object 
# table <- list()
# table$percent_unknown_disturbence_event <- dim(unknowns)[1]/dim(final)[1]
# table$percent_unknown_single_area <- sum(unknown_only$size_ha)/ sum(final$size_ha)
# table$percent_unknown_single_event <-  dim(unknown_only)[1]/dim(final)[1]
 #table$pecent_mixed_disturbence_event <- dim(mixed_disturbence)[1] /dim(final)[1]
#pecent_mixed_disturbence_event <- dim(mixed_disturbence)[1] /dim(final)[1]
# table$percent_unknown_area <- sum(unknowns$size_ha) / sum(final$size_ha)
# table$pecent_mixed_disturbence_area <- sum(mixed_disturbence$size_ha) / sum(final$size_ha)
#pecent_mixed_disturbence_area <- sum(mixed_disturbence$size_ha) / sum(final$size_ha)
# table$percent_mixed_no_unknows <- sum(no_unknowns_mixed_disturbence$size_ha)/ sum(final$size_ha)
# print(table)
# table$percent_mixed_no_unknowns_event <- dim(no_unknowns_mixed_disturbence)[1]/dim(final)[1]

pecent_mixed_disturbence_event <- dim(mixed_disturbence)[1] /dim(final)[1]
pecent_mixed_disturbence_area <- sum(mixed_disturbence$size_ha) / sum(final$size_ha)

percent_unknown_single_event <-  dim(unknown_only)[1]/dim(final)[1]
percent_unknown_single_area <- sum(unknown_only$size_ha)/ sum(final$size_ha)


options(sig = 10)
## Print out Disturbence area percentage and event percentage 
for(i in seq_along(all_disturbences)){
  
  subset <- single_disturbence[single_disturbence$dist_name == all_disturbences[i], ]
  percent_event <- dim(subset)[1] / dim(final)[1]
  percent_area <- sum(na.omit(subset$size_ha))/ sum(na.omit(final$size_ha))
  number  <- length(subset$clno)
  print(paste(all_disturbences[i], ":", "Percent event:", percent_event, "Percent area:", percent_area, "N of: ", number ))
  
}

## State and ecoregions

length(final[final$state == "FL",]$size_ha)/length(final$size_ha)
sum(final[final$state == "FL",]$size_ha)/sum(final$size_ha)

length(final[final$eco_II == "8.3",]$size_ha)/length(final$size_ha)
sum(final[final$eco_II == "8.3",]$size_ha)/sum(final$size_ha)

length(final[final$eco_II == "8.5",]$size_ha)/length(final$size_ha)
sum(final[final$eco_II == "8.5",]$size_ha)/sum(final$size_ha)



length(final[final$state == "OR",]$size_ha)/length(final$size_ha)
sum(final[final$state == "OR",]$size_ha)/sum(final$size_ha)

length(final[final$eco_II == 6.2,]$size_ha)/length(final$size_ha)
sum(final[final$eco_II == 6.2,]$size_ha)/sum(final$size_ha)

length(final[final$eco_II == 7.1,]$size_ha)/length(final$size_ha)
sum(final[final$eco_II == 7.1,]$size_ha)/sum(final$size_ha)

```
# Decriptive Statistics for Mixed disturbences

```{r}
## A co-occurence matrix of Disturbences in mixed disturbneces
names_of_mixed <- mixed_disturbence$dist_name
tmp_names <- strsplit(as.character(names_of_mixed), split = ", ")
mixed_names <- unlist(tmp_names)

heatmap <- matrix(nrow = 14, ncol = 14)
heatmap[is.na(heatmap)] <- 0
heatmap <- as.data.frame(heatmap)
colnames(heatmap) <- unique(mixed_names)
rownames(heatmap) <- unique(mixed_names)

for (i in 1:length(tmp_names)){
  length <- length(tmp_names[[i]])
  for (j in 1: length){
    dist_y <- tmp_names[[i]][j]
    for(k in 1:length){
      dist_x <- tmp_names[[i]][k]
      heatmap[dist_y, dist_x] <- heatmap[dist_y, dist_x] +1
    }
    
  }
  
}

heatmap <- as.matrix(heatmap)
 get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
 }
 heatmap <- get_lower_tri(heatmap)
 


library(reshape2)
melted <- melt(heatmap)
melted

ggheatmap <- ggplot(melted, aes(Var2, Var1, fill = log(value)))+
 geom_tile(color = "grey")+
 scale_fill_gradient2(low = "white", high = "blue",
    #space = "Lab", 
    name="Co-ocurence", na.value="white") +
  theme_minimal()+ # minimal theme
 # scale_x_continuous(trans="log")+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1), axis.text.y = element_text( size = 12))+
 coord_fixed()+ 
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 3) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border =element_blank(),
  #panel.background = element_rect(fill = "white"), #element_blank(),
  axis.ticks = element_blank(),
  legend.position ="none"
  )+
  ggtitle("Co-Occurence Within Mixed Disturbances")

ggheatmap

```

# Density Figures

```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)

## Ecoregion in ggridges
#density_ecoregions <- na.omit(single_disturbence[single_disturbence$dist_name %in% disturbences_names, ]) %>%

#density_ecoregions <- single_disturbence %>%
final$size_ha <- as.numeric(final$size_ha)
density_ecoregions <- final %>%
ggplot(aes(x = size_ha, y = eco_II, fill = eco_II)) + scale_x_continuous(trans="log")+
  geom_density_ridges() +
  geom_vline(xintercept = 0.09)+
theme(panel.background = element_blank(), 
      plot.background = element_rect(fill = "transparent", color = NA),
      axis.text.y = element_blank(), 
      axis.title.y = element_blank(), 
      axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      legend.position = "none"
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size ha") + 
  #ggtitle("Ecoregion")+
  scale_fill_manual(values= eco_region_colors)  
  density_ecoregions

# 800 461
density_ecoregions
ggsave(density_ecoregions, filename = "density_ecoregions.png", bg="transparent", width = 800, height = 461, units = "mm")


### Disturbence Density Plots 
#density_disturbence <- na.omit(single_disturbence[single_disturbence$dist_name %in% disturbences_names, ]) %>%
#density_disturbence <- single_disturbence %>%
density_disturbence <- final[final$dist_name2 %in% all_disturbences,]%>%
ggplot( aes(x = size_ha, y = dist_name2, fill = dist_name2)) + scale_x_continuous(trans="log", limits = 0.09)+ geom_density_ridges() +
  geom_vline(xintercept = 0.09)+
theme(panel.background = element_blank(), 
      plot.background = element_rect(fill = "transparent", color = NA),
      axis.text.y = element_blank(), 
      axis.title.y = element_blank(), 
      axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      legend.position = "none"
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size ha") +
  #ggtitle("Size Distributions")+
  scale_fill_manual(values= disturbence_colors_all)

density_disturbence
 ggsave(density_disturbence, filename = "density_disturbence.png", bg="transparent")

```


# KS tests for Supplemental Table 2

The Kolmogorov–Smirnov test we ran included single pixel, double pixel, and triple pixels unlike the Maximum Likelihood tests, where single, double and triple pixel -sized disturbences were excluded (See below). 

Initialy, we just ran KS tests on disturbence size distributions that were also included in the size distribution by interior-totel ratio curve fits and likelyhood-ratio test comparison. Because the liklyhood ratio test requires strict subsetting, we eliminated all disturbences that weren't present in all four ecoregions. KS tests don't have the same requirements, so here we explore the wider range of size distributions present in the dataset. We treat mixed disturbances as an independant type of disturbance. 

```{r, echo=TRUE, message=FALSE, warning=FALSE}

### Making Disturbence-level objects
fire_only <- single_disturbence[grep("ire", single_disturbence$dist_name),]
wildland <- fire_only[grep("Wildland", fire_only$dist_name),]
wildfire <- fire_only[grep("Wildfire", fire_only$dist_name),]
Prescribed <- fire_only[grep("Prescribed Fire", fire_only$dist_name),]

prescribed <- Prescribed
clearcut_only <- single_disturbence[grep("Clear", single_disturbence$dist_name),]
#herbicide_only <- single_disturbence[grep("Herbicide", single_disturbence$dist_name),]

thining_only <- single_disturbence[grep("Thinning", single_disturbence$dist_name),]
other_mechanical <- single_disturbence[grep("Other Mechanical", single_disturbence$dist_name),]
mastication <- single_disturbence[single_disturbence$dist_name == "Mastication",]
herbicide <- single_disturbence[single_disturbence$dist_name == "Herbicide",]
unknown_only <- unknown_only
harvest <- single_disturbence[single_disturbence$dist_name == "Harvest",]
#biological <- single_disturbence[single_disturbence$dist_name == "Biological",]
chemical <- single_disturbence[single_disturbence$dist_name == "Chemical",]
#disease <- single_disturbence[single_disturbence$dist_name == "Disease",]
mixed <- final[final$dist_name2 == "Mixed",]

options(digits = 3)
dist_size<-list(clearcut_only$sizw, wildland$sizw, wildfire$sizw, prescribed$sizw, thining_only$sizw, other_mechanical$sizw, as.numeric(unknown_only$sizw), herbicide$sizw, mastication$sizw, as.numeric(harvest$sizw), as.numeric(chemical$sizw), as.numeric(mixed$sizw) )

names(dist_size) <- c("Clearcut", "Wildland Fire", "Wildfire", "Prescribed", "Thinning","Other mechanical", "Unknown", "Herbicide", "Mastication", "Harvest", "Chemical",  "Mixed" )

size_dist_resulsts <- list()

iterator <- 0
for ( i in 1:length(names(dist_size))){
  for (j in 1:length(names(dist_size))){
    print(paste(names(dist_size)[i], "x", names(dist_size)[j]))
    iterator <- iterator + 1
    results <- ks.test(dist_size[[i]],dist_size[[j]], alternative = "two.sided")
    results$names <- paste(names(dist_size)[i], "x", names(dist_size)[j])
    size_dist_resulsts[[iterator]] <- results
  }
}
 
options(digits = 3)
sig <- rep(NA, length(names(dist_size))^2)
KS_results <- list()
KS_results$combination  <- rep(NA, length(names(dist_size))^2)
KS_results$pval <- rep(NA, length(names(dist_size))^2)
KS_results$sig <- rep(NA, length(names(dist_size))^2)
KS_results$D <- rep(NA, length(names(dist_size))^2)
 KS_results <- as.data.frame(KS_results)

for (i in 1:(length(names(dist_size))^2)){

  KS_results$pval[i] <- size_dist_resulsts[[i]]$p.value
  KS_results$combination[i] <- paste(size_dist_resulsts[[i]]$names)
  KS_results$sig[i] <- FALSE
  KS_results$D[i] <- size_dist_resulsts[[i]]$statistic
 
  ## Build # of pairwise comparisons function for the calculation of p.val
  pairs <- function (num){
    result <- (num*(num-1))/2
    return(result)
  }
  
  Bonf_val <- 0.05/ (pairs(length(all_disturbences)) + 3) # Plus 3 for states and ecoregions
  
  if(size_dist_resulsts[[i]]$p.value < Bonf_val) { 
   sig[i] <- paste(size_dist_resulsts[[i]]$names)
   KS_results$sig[i] <- TRUE
   print("Found one!")
  }
    
}
 KS_results <- as.list(KS_results)
state_size <- ks.test(as.numeric(single_disturbence[single_disturbence$state == "OR",]$sizw), as.numeric(single_disturbence[single_disturbence$state == "FL",]$sizw ))

KS_results$combination[length(names(dist_size))^2 +1] <- "Oregon x Florida"
KS_results$pval[length(names(dist_size))^2 +1] <- state_size$p.value
KS_results$sig[length(names(dist_size))^2 +1] <-  state_size$p.value < Bonf_val
KS_results$D[length(names(dist_size))^2 +1] <- state_size$statistic

fl_8_3_8_5 <- ks.test(as.numeric(single_disturbence[single_disturbence$eco_II == "8.5",]$sizw), as.numeric(single_disturbence[single_disturbence$eco_II == "8.3",]$sizw ))
or_6_2_7_1 <- ks.test(as.numeric(single_disturbence[single_disturbence$eco_II == "6.2",]$sizw), as.numeric(single_disturbence[single_disturbence$eco_II == "7.1",]$sizw ))

KS_results$combination[length(names(dist_size))^2 +2] <- paste("8.5 x 8.3")
KS_results$pval[length(names(dist_size))^2 +2] <- fl_8_3_8_5$p.value
KS_results$sig[length(names(dist_size))^2 +2] <-  fl_8_3_8_5$p.value < Bonf_val
KS_results$D[length(names(dist_size))^2 +2] <- fl_8_3_8_5$statistic

KS_results$combination[length(names(dist_size))^2 +3] <- paste("6.2 x 7.1")
KS_results$pval[length(names(dist_size))^2 +3] <- or_6_2_7_1$p.value
KS_results$sig[length(names(dist_size))^2 +3] <-  or_6_2_7_1$p.value < Bonf_val
KS_results$D[length(names(dist_size))^2 +3] <- or_6_2_7_1$statistic


KS_results <- as.data.frame(KS_results)
KS_results <- KS_results[KS_results$pval != 1, ]

### Make table with results 
options(knitr.table.format = "html")

KS_results[,c(1:2, 4)] %>%
 # select(combination, pval, D) %>%
 kable(  booktabs = T, escape = F, digits = 5, row.names = FALSE, col.names = c("Comparison", "P value", "D statistic")) %>%
  kable_styling(latex_options = "striped", full_width = F) %>%
  #select(KS_results$sig == TRUE) %>%
  row_spec(which(KS_results$sig), bold = T, background = "#ADD8E6")# %>%
  
write.csv2(KS_results, row.names = FALSE, file = "Mixed_included_results_2018.csv")


```

# Plotting Disturbence-level Abundance

This figure didn't make it into the paper, but is another _non MLE_ visualization tool. 

```{r}

## Making the upper and lower bounds
length <- length(single_disturbence[hex_conditional,]$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence[hex_conditional,]$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)

other_dists <- all_disturbences[!all_disturbences %in% disturbences_names]

### Disturbances hex only
hex_conditional <- single_disturbence$sizw > 3 & single_disturbence$dist_name %in% other_dists

disturbences_abundence <- single_disturbence[hex_conditional, ] %>%
ggplot( show.legend = FALSE) +
  geom_hex(aes(sizw, ratio, color = dist_name)) + 
  geom_line(aes(x =seq   , y = (upper )), color = "black")+
  geom_line(aes(x =seq  , y = (lower )), color = "black")+
scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log",   low = "#bdbdbd", high = "#636363") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      axis.title.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      legend.title = element_blank()
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("All Disturbances") + 
  scale_color_manual(values= color_cheat_sheet[color_cheat_sheet$dist %in% other_dists,]$colors)+
  xlab("Area ha") +
  ylab("Interior / Total Ratio ")+ 
  ggtitle("Disturbance Types")+
  theme(panel.background = element_rect(fill = "transparent") # bg of the panel
    , plot.background = element_rect(fill = "transparent", color = NA),      legend.background = element_rect(fill = "transparent")
    , legend.box.background = element_rect(fill = "transparent"))
disturbences_abundence

# ggsave(disturbences_abundence, filename = #"disturbences_abundence.png", bg="transparent")
 

```

# Choosing parameter sets from sensitivity analysis

```{r}
## read in objects from Sensitivity_of_MLE fits files
state_to_null_output <- read.csv("/Users/tess/Documents/work/Spacial_adj/MLE_Analysis/fixed_state_to_null_output.csv") 
eco_to_state_output <- read.csv("/Users/tess/Documents/work/Spacial_adj/MLE_Analysis/fixed_eco_to_state_output.csv")
disturbence_to_null_output <- read.csv("/Users/tess/Documents/work/Spacial_adj/MLE_Analysis/fixed_disturbance_to_null_output.csv")

## Making pottable objects with qa/qc filtering
state_params <- state_to_null_output %>%
                filter(all_converge == TRUE)  %>%
                filter(valid_subset == TRUE) 
state_params <- state_params[state_params$tmt_l == min(state_params$tmt_l),]

florida_param <- strsplit(as.character(state_params$florida_param[1]), split = ",")
florida_param <- unlist(florida_param)

eco_state_params <- eco_to_state_output %>%
                filter(all_converge == TRUE)  %>%
                filter(valid_subset == TRUE) 
eco_state_params <- eco_state_params[eco_state_params$tmt_l == min(eco_state_params$tmt_l),]

fl_8_3 <- strsplit(as.character(eco_state_params$fl_8_3_param[1]), split = ",")
fl_8_3  <- unlist(fl_8_3)
fl_8_3  <- as.numeric(fl_8_3)

fl_8_5 <- strsplit(as.character(eco_state_params$fl_8_5_param[1]), split = ",")
fl_8_5 <- unlist(fl_8_5)
fl_8_5 <- as.numeric(fl_8_5)
or_7_1 <- strsplit(as.character(eco_state_params$or_7_1_param[1]), split = ",")
or_7_1 <- unlist(or_7_1)
or_7_1 <- as.numeric(or_7_1)

or_6_2 <- strsplit(as.character(eco_state_params$or_6_2_param[1]), split = ",")
or_6_2 <- unlist(or_6_2)
or_6_2 <- as.numeric(or_6_2)


if (length(unique(eco_state_params$pval)) > 1 ){ ## Double check that differences in null MLE doesn't affect the pval
  print("ERROR SIGNIFICANCE AFFECTED BY OPTIM")
  eco_state_params <- NULL
}

disturbence_params <- disturbence_to_null_output  %>%
                filter(all_converge == TRUE)  %>%
                filter(valid_subset == TRUE) %>%
                filter(method == "L-BFGS-B")
disturbence_params <- disturbence_params[disturbence_params$tmt_l == min(disturbence_params$tmt_l),]

if (length(unique(disturbence_params$pval)) > 1 ){ ## Double check that differences in null MLE doesn't affect the pval
  print("ERROR SIGNIFICANCE AFFECTED BY OPTIM")
  disturbence_params <- NULL
}

## Make list of each disturbance parameter set
col_list <- grep("param", names(disturbence_params))

all_dist <- list()
for( i in 1:length(grep("param", names(disturbence_params)))){
  col <- disturbence_params[, col_list[i]]
  tmp <- strsplit(as.character(col[1]), split = ",")
  tmp <- unlist(tmp)
  tmp <- as.numeric(tmp)
  all_dist[[i]] <- tmp
  as.data.frame(all_dist[[i]])
  names(all_dist[[i]]) <- names(disturbence_params)[col_list[i]]
  #names(all_dist[[i]]) <- names(disturbence_params)[i]
  #print(names(all_dist[[i]]))
}

#state_to_disturbence_params <- state_to_disturbence_output %>%
#                            filter(all_converge == TRUE)  %>%
#                            filter(valid_subset == TRUE) 
#state_to_disturbence_params <- state_to_disturbence_params[state_to_disturbence_params$tmt_1 == min(state_to_disturbence_params$tmt_1),] ## Not Significant



```

## Double Are Florida's curves really different? 

```{r}
### Is Florida significantly different when evaluated seperatly? (Note, had to load objects from sensitivity_of_MLE_fits)

## Compare? 

    dev.null <-   2*florida_param$value ## tmt from previous analysis MUCH EASIER IF PASSED
    dev.tmt  <- 2*fl_8_3$value + 2*fl_8_5$value   # 8 params in the null, 16 - 4
    LR       <- dev.null - dev.tmt        ## Likelihood ratio
    pval     <- 1 - pchisq(LR,4)
    pval 

    
### Is Oregon significantly different when evaluated seperatly? 
    
dev.null <-   2*oregon_param$value ## tmt from previous analysis MUCH EASIER IF PASSED
    dev.tmt  <- 2* or_6_2$value + 2*or_7_1$value   # 8 params in the null, 16 - 4
    LR       <- dev.null - dev.tmt        ## Likelihood ratio
    pval     <- 1 - pchisq(LR,4)
    pval 

```

## Ploting curves of interior/total ratio


# Ecoregion within state

```{r, echo=TRUE, message=FALSE, warning=FALSE}

length <- length(single_disturbence[null_model_conditional & single_disturbence$state == "FL",]$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence[null_model_conditional,]$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)

### State based figures
#final %>% 
  #filter(state == "FL") %>%
florida_plot <- single_disturbence[null_model_conditional & single_disturbence$state == "FL",] %>%
ggplot(aes(sizw, ratio), show.legend = TRUE) +
  geom_hex() + 
  geom_line(aes(x =seq  , y = (upper )), color = "black")+
  geom_line(aes(x =seq , y = (lower )), color = "black") +
  geom_line(aes(x = seq, y = ( fl_8_3[2]*seq^fl_8_3[3])/(fl_8_3[1] + seq^fl_8_3[3]) ), color = eco_region_colors[4])+ #plotting fl_8_3
  geom_line(aes(x = seq, y = (fl_8_5[2]*seq^fl_8_5[3])/(fl_8_5[1] + seq^fl_8_5[3]) ), color = eco_region_colors[3])+ #plotting fl_8_5
  scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log", breaks = c(1,10,100, 500),  high = "#636363", low = "#bdbdbd") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      #axis.title.y = element_blank(),
      #axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      legend.title = element_blank()
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Area ha") +
  ylab("Interior / Total ratio")+ 
  ggtitle("Florida")+
  theme(panel.background = element_rect(fill = "transparent") # bg of the panel
    , plot.background = element_rect(fill = "transparent", color = NA),        legend.background = element_rect(fill = "transparent")
    , legend.box.background = element_rect(fill = "transparent"))

#ggsave(florida_plot, filename = "florida_plot.png", bg ="transparent")


length <- length(single_disturbence[null_model_conditional & single_disturbence$state == "OR",]$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence[null_model_conditional,]$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)

## State-based figures
#final %>% 
  #filter(state == "FL") %>%
oregon_plot <- single_disturbence[null_model_conditional & single_disturbence$state == "OR",] %>%
ggplot(aes(sizw, ratio), show.legend = TRUE) +
  geom_hex() + 
  geom_line(aes(x =seq  , y = (upper )), color = "black")+
  geom_line(aes(x =seq , y = (lower )), color = "black")+
  geom_line(aes(x = seq, y = ( or_6_2[2]*seq^or_6_2[3])/(or_6_2[1] + seq^or_6_2[3]) ), color = eco_region_colors[1])+ # 6.2
  geom_line(aes(x = seq, y = (or_7_1[2]*seq^or_7_1[3])/(or_7_1[1] + seq^or_7_1[3]) ), color = eco_region_colors[2])+ # 7.1
   scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log", breaks = c(1,10,100, 500),  high = "#636363", low = "#bdbdbd") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      #axis.title.y = element_blank(),
      #axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      legend.title = element_blank()
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Area ha") +
  ylab("Interior / Total ratio")+ 
  ggtitle("Oregon")+
  theme(panel.background = element_rect(fill = "transparent") # bg of the panel
    , plot.background = element_rect(fill = "transparent", color = NA),        legend.background = element_rect(fill = "transparent")
    , legend.box.background = element_rect(fill = "transparent"))

#ggsave(oregon_plot, filename = "oregon_plot.png", bg ="transparent")
```


# Disturbence curves
 
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(gridExtra)
library(grid)
dist_order <- c("Unknown", "Other Mechanical", "Prescribed Fire", "Wildfire", "Thinning", "Herbicide", "Clearcut")

### Disturbance Model lines
length <- length(single_disturbence$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)


disturbence_plot <- single_disturbence %>%
ggplot(aes(sizw, ratio), show.legend = TRUE) +
  geom_hex(data = single_disturbence[null_model_conditional, ],aes(sizw, ratio)) + 
  geom_line(aes(x =seq   , y = (upper )), color = "black")+
  geom_line(aes(x =seq  , y = (lower )), color = "black")+


## Plot disturbence lines
 geom_line(aes(x =seq, (all_dist[[1]][2]*seq^all_dist[[1]][3])/(all_dist[[1]][1] + seq^all_dist[[1]][3])), color = color_cheat_sheet[color_cheat_sheet$dist == dist_order[1],]$colors)+ #5
   geom_line(aes(x =seq, (all_dist[[2]][2]*seq^all_dist[[2]][3])/(all_dist[[2]][1] + seq^all_dist[[2]][3])), color = color_cheat_sheet[color_cheat_sheet$dist == dist_order[2],]$colors)+
   geom_line(aes(x =seq, (all_dist[[3]][2]*seq^all_dist[[3]][3])/(all_dist[[3]][1] + seq^all_dist[[3]][3]) ), color = color_cheat_sheet[color_cheat_sheet$dist == dist_order[3],]$colors )+
   geom_line(aes(x =seq, (all_dist[[4]][2]*seq^all_dist[[4]][3])/(all_dist[[4]][1] + seq^all_dist[[4]][3])), color = color_cheat_sheet[color_cheat_sheet$dist == dist_order[4],]$colors)+
   geom_line(aes(x =seq, (all_dist[[5]][2]*seq^all_dist[[5]][3])/(all_dist[[6]][1] + seq^all_dist[[5]][3])), color = color_cheat_sheet[color_cheat_sheet$dist == dist_order[5],]$colors)+
   geom_line(aes(x =seq, (all_dist[[6]][2]*seq^all_dist[[6]][3])/(all_dist[[6]][1] + seq^all_dist[[6]][3])), color = color_cheat_sheet[color_cheat_sheet$dist == dist_order[6],]$colors)+
    geom_line(aes(x =seq, (all_dist[[7]][2]*seq^all_dist[[7]][3])/(all_dist[[7]][1] + seq^all_dist[[7]][3])), color = color_cheat_sheet[color_cheat_sheet$dist == dist_order[7],]$colors)+
  
scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log", breaks = c(1,10,100, 500),  high = "#636363", low = "#bdbdbd") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      #axis.title.y = element_blank(),
      #axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      #legend.position= "none"
      legend.title = element_blank()
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size (ha)") + 
  scale_color_manual(values= disturbence_colors)+
  xlab("Area ha") +
  ylab("Interior / Total Ratio ")+ 
  ggtitle("All Disturbances")+
  theme(panel.background = element_rect(fill = "transparent") # bg of the panel
    , plot.background = element_rect(fill = "transparent", color = NA),      legend.background = element_rect(fill = "transparent")
    , legend.box.background = element_rect(fill = "transparent"))

ggsave(disturbence_plot, filename = "disturbence_plot.png", bg ="transparent")

```

# Plot Disturbance Curves Individually with data fits

```{r}

#plot <- list()

length <- length(single_disturbence$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)

## Sequence over all the lines individually

for(i in seq_along(dist_order)){

  
plot <- single_disturbence %>%
 ggplot(aes(sizw, ratio), show.legend = TRUE) +
  geom_hex(data = single_disturbence[null_model_conditional & single_disturbence$dist_name == dist_order[i], ], aes(sizw, ratio)) +
  geom_line( aes(x =seq   , y = (upper )), color = "black")+
  geom_line( aes(x =seq  , y = (lower )), color = "black")+
 geom_line( aes(x =seq, (all_dist[[i]][2]*seq^all_dist[[i]][3])/(all_dist[[i]][1] + seq^all_dist[[i]][3]) ), color = "black")+

scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log", high = "#636363", low = "#bdbdbd") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      #axis.title.y = element_blank(),
      #axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      #legend.position= "none"
      legend.title = element_blank()
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size (ha)") + 
  #scale_color_manual(values= disturbence_colors)+
  xlab("Area ha") +
  ylab("Interior / Total Ratio ")+ 
  ggtitle(dist_order[i])+
  theme(panel.background = element_rect(fill = "transparent") # bg of the panel
    , plot.background = element_rect(fill = "transparent", color = NA),      legend.background = element_rect(fill = "transparent")
    , legend.box.background = element_rect(fill = "transparent"))

ggsave(plot, filename = paste(dist_order[i], "_plot.png", sep =""), bg ="transparent")

}


```









