---
title: "Empirical Analyses"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(MASS)
library(ggridges)
```

# read in data

```{r, echo= TRUE, message=FALSE, warning=FALSE}

florida_8_3 <- read.csv("~/Documents/work/Spacial_adj/Data_and_Figures/Florida_fixed_8_3_2014dm2.csv", header = TRUE)
florida_8_5 <- read.csv("~/Documents/work/Spacial_adj/Data_and_Figures/Florida_fixed_8_5_2014dm2.csv", header = TRUE)
  
oregon_6_2 <- read.csv("~/Documents/work/Spacial_adj/Data_and_Figures/Oregon_fixed__6_2_2014dm2.csv", header = TRUE)
oregon_7_1 <-  read.csv("~/Documents/work/Spacial_adj/Data_and_Figures/Oregon_fixed__7_1_2014dm2.csv", header = TRUE)
```

# Upper + lower interior/ total ratio Helper functions

These functions provide the bounds on upper and lower interior / total ratios for different numbers of pixels. 

```{r, echo=TRUE, message=FALSE, warning=FALSE}

upper_bound_ratios <- function(x){
  upper <- rep(NA, length(x))
  edge <- rep(NA, length(x))
  interior <- rep(NA, length(x))
  
  ## get edges
  for(i in seq_along(x)){
    smaller_sqrt <- floor(sqrt(x[i]))
    smaller_square <- smaller_sqrt^2
    
    larger_sqrt <- ceiling(sqrt(x[i]))
    
    remainder <- x[i] %% smaller_square
    
    if (remainder > smaller_sqrt){
      edge[i] <- 4 * larger_sqrt
    }
    
    if (remainder <= smaller_sqrt){
      edge[i] <- (2*smaller_sqrt) + 2*(1+smaller_sqrt)
    }
    
    if (remainder == 0){
      edge[i] <- 4 * larger_sqrt
    }
  }
  
  #get interiors
  for (i in seq_along(x)){
    interior[i] <- 4 * x[i]
    interior[i] <- interior[i] - edge[i]
  }
  
  for (i in seq_along(x)){
    if (x[i] == 1){
      upper[i] <- 0
      next  
    }
    if (x[i] == 2){
      upper[i] <- 0.25
      next
    }
    if (x[i] == 3){
      upper[i] <- 0.5
      next 
    }
    
    upper[i] <- interior[i] / (interior[i] + edge[i])
  }
  
  
  return(upper)
}

lower_bound_ratios <- function(x){
  lower <- rep(NA, length(x))
  edge <- rep(NA, length(x))
  interior <- rep(NA, length(x))
  
  for (i in seq_along(x)){
    if(x[i] == 1){
      edge[i] <- 4
      next
    }
    
    if (x[i] == 2){
      edge[i] <- 6  
      next
    }
    
      edge[i] <- (2 * (x[i] - 2)) + 6 # The six accounts for sides of the two end pixels 
  }
  
  for (i in seq_along(x)){
    if(x[i] == 1){
    interior[i] <- 0
     lower[i] <- interior[i] / (interior[i] + edge[i])
      next
    }
    
    if (x[i] == 2){
     interior[i] <- 2
      lower[i] <- interior[i] / (interior[i] + edge[i])
      next
    }
    
     interior[i] <- ((4 * x[i]) - edge[i])
     lower[i] <- interior[i] / (interior[i] + edge[i])
  }
  return (lower)
}


```

# Sifting out edge-cases with artificial ratio inflation

The base raster adjacency function that we used when calculating interior/total ratios made a wrap-around adjacency assumption, inflating the adjacency of corner and edge pixels. We corrected for it by setting ratios above the maximum to NA. 

```{r, echo=TRUE, message=FALSE, warning=FALSE}
oregon_6_2$eco_II <- "6.2"  ## Put in Ecoregion labels 
oregon_7_1$eco_II <- "7.1"
florida_8_3$eco_II <- "8.3"
florida_8_5$eco_II <- "8.5"

florida <- rbind(florida_8_3, florida_8_5) 
oregon <- rbind(oregon_6_2, oregon_7_1)

florida$size_ha <- florida$sizw * 0.09  ## Convert Pixels to ha
oregon$size_ha <- oregon$sizw * 0.09

florida$state <- "FL"  ## State Labels 
oregon$state <- "OR"
final <- rbind(florida, oregon)


final$ratio[(final$ratio > 0.25) & (final$sizw == 2)] <- NA
final$ratio[(final$ratio > 0.33) & (final$sizw == 3)] <- NA
final$ratio[(final$ratio > 0.50) & (final$sizw == 4)] <- NA
final$ratio[(final$ratio > 0.5 ) & (final$sizw == 5)] <- NA
final$ratio[(final$ratio > 0.55333333) & (final$sizw == 6)] <- NA
final$ratio[(final$ratio > 0.5714286) & (final$sizw == 7)] <- NA
final$ratio[(final$ratio >  0.7083333) & (final$sizw == 12)] <- NA
final$ratio[(final$ratio >  0.7631579) & (final$sizw == 19)] <- NA

```


## Analyses & Descriptive statistics

# Subset Dataset for percentenge estimates of mixed disturbence types, and unknowns

```{r, echo=TRUE, message=FALSE, warning=FALSE}

unknowns <- final[grep("Unknown", final$dist_name) ,]   
no_unknowns <- dplyr::anti_join(final, unknowns, by = "dist_name") 
mixed_disturbence <- final[grep(",", final$dist_name), ]
single_disturbence <- dplyr::anti_join(final, mixed_disturbence, by = "dist_name")

single_disturbence <- na.omit(single_disturbence)

no_unknowns_mixed_disturbence <- dplyr::anti_join(mixed_disturbence, unknowns, by = "dist_name") 
no_unknowns_single_disturbence <- dplyr::anti_join(single_disturbence, unknowns, by = "dist_name")
unknown_only <- dplyr::anti_join(unknowns, mixed_disturbence, by = "dist_name")

```

```{r}
dist_8_3 <- unique(single_disturbence[single_disturbence$eco_II == 8.3,]$dist_name)
dist_8_5 <- unique(single_disturbence[single_disturbence$eco_II == 8.5,]$dist_name)
dist_7_1 <- unique(single_disturbence[single_disturbence$eco_II == 7.1,]$dist_name)
dist_6_2 <- unique(single_disturbence[single_disturbence$eco_II == 6.2,]$dist_name)

common_disturbences <- Reduce(intersect, list(dist_8_3,dist_8_5,dist_7_1, dist_6_2))
common_disturbences <- common_disturbences[common_disturbences != ""]

disturbences_names <-  common_disturbences # These are the disturbences that are common between 4 ecoregions

## Set up common color schemes 

disturbence_colors <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f')   #,'#ff7f00','#cab2d6')

eco_region_colors <- c('#df65b0', '#67001f', '#081d58','#7fcdbb') # Oregon then Florida

state_colors <- c('#980043', "#225ea8")
```



# Estimate qa/qc stats for supplemental table 1

```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(lemon)
library(knitr)

## Estimate unknown disturbence in an object 
# table <- list()
# table$percent_unknown_disturbence_event <- dim(unknowns)[1]/dim(final)[1]
# table$percent_unknown_single_area <- sum(unknown_only$size_ha)/ sum(final$size_ha)
# table$percent_unknown_single_event <-  dim(unknown_only)[1]/dim(final)[1]
# table$pecent_mixed_disturbence_event <- dim(mixed_disturbence)[1] /dim(final)[1]
# table$percent_unknown_area <- sum(unknowns$size_ha) / sum(final$size_ha)
# table$pecent_mixed_disturbence_area <- sum(mixed_disturbence$size_ha) / sum(final$size_ha)
# table$percent_mixed_no_unknows <- sum(no_unknowns_mixed_disturbence$size_ha)/ sum(final$size_ha)
# print(table)
# table$percent_mixed_no_unknowns_event <- dim(no_unknowns_mixed_disturbence)[1]/dim(final)[1]


## Print out Disturbence area percentage and event percentage 
for(i in seq_along(disturbences_names)){
  subset <- single_disturbence[single_disturbence$dist_name == disturbences_names[i], ]
  percent_event <- dim(subset)[1] / dim(final)[1]
  percent_area <- sum(na.omit(subset$size_ha))/ sum(na.omit(final$size_ha))
  
  print(paste(disturbences_names[i], ":", "Pecent event:", percent_event, "Percent area:", percent_area ))
  
}



```


# Density Figures

```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)

## Ecoregion in ggridges
  na.omit(single_disturbence[single_disturbence$dist_name %in% disturbences_names, ]) %>%
ggplot( aes(x = size_ha, y = eco_II, fill = eco_II)) + scale_x_continuous(trans="log")+ geom_density_ridges() +
  geom_vline(xintercept = 0.09)+
theme(panel.background = element_blank(), 
      axis.text.y = element_blank(), 
      axis.title.y = element_blank(), 
      axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      legend.position = "none"
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size ha") + 
    #ggtitle("Ecoregion")+
  scale_fill_manual(values= eco_region_colors)  
  
### Disturbence Density Plots 
na.omit(single_disturbence[single_disturbence$dist_name %in% disturbences_names, ]) %>%
ggplot( aes(x = size_ha, y = dist_name, fill = dist_name)) + scale_x_continuous(trans="log", limits = 0.09)+ geom_density_ridges() +
  geom_vline(xintercept = 0.09)+
theme(panel.background = element_blank(),
      axis.text.y = element_blank(),
      axis.title.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      legend.position = "none"
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size ha") + 
  #ggtitle("Size Distributions")+
  scale_fill_manual(values= disturbence_colors)  

```


# KS tests for Supplemental Table 2

The Kolmogorov–Smirnov test we ran included single pixel, double pixel, and triple pixels unlike the Maximum Likelihood tests, where those were excluded (See below). 

```{r, echo=TRUE, message=FALSE, warning=FALSE}

### Making Disturbence-level objects
fire_only <- single_disturbence[grep("ire", single_disturbence$dist_name),]
#wildland <- fire_only[grep("Wildland", fire_only$dist_name),]
wildfire <- fire_only[grep("Wildfire", fire_only$dist_name),]
Prescribed <- fire_only[grep("Prescribed Fire", fire_only$dist_name),]

prescribed <- Prescribed
clearcut_only <- single_disturbence[grep("Clear", single_disturbence$dist_name),]
herbicide_only <- single_disturbence[grep("Herbicide", single_disturbence$dist_name),]
thining_only <- single_disturbence[grep("Thinning", single_disturbence$dist_name),]
other_mechanical <- single_disturbence[grep("Other Mechanical", single_disturbence$dist_name),]
#mastication <- single_disturbence[single_disturbence$dist_name == "Mastication",]
herbicide <- single_disturbence[single_disturbence$dist_name == "Herbicide",]
unknown_only <- unknown_only


options(digits = 3)
dist_size<-list(clearcut_only$sizw, wildfire$sizw, prescribed$sizw, thining_only$sizw, other_mechanical$sizw, unknown_only$sizw, herbicide$sizw)
names(dist_size) <- c("Clearcut", "Wildland Fire", "Wildfire", "Prescribed", "Thinning","Other mechanical", "Unknown")

size_dist_resulsts <- list()

iterator <- 0
for ( i in 1:length(names(dist_size))){
  for (j in 1:length(names(dist_size))){
    iterator <- iterator + 1
    results <- ks.test(dist_size[[i]],dist_size[[j]], alternative = "two.sided")
    results$names <- paste(names(dist_size)[i], "x", names(dist_size)[j])
    size_dist_resulsts[[iterator]] <- results
  }
}
 
options(digits = 3)
sig <- rep(NA, length(names(dist_size))^2)
KS_results <- list()
KS_results$combination  <- rep(NA, length(names(dist_size))^2)
KS_results$pval <- rep(NA, length(names(dist_size))^2)
KS_results$sig <- rep(NA, length(names(dist_size))^2)
KS_results$D <- rep(NA, length(names(dist_size))^2)
 KS_results <- as.data.frame(KS_results)

for (i in 1:(length(names(dist_size))^2)){

  KS_results$pval[i] <- size_dist_resulsts[[i]]$p.value
  KS_results$combination[i] <- paste(size_dist_resulsts[[i]]$names)
  KS_results$sig[i] <- FALSE
  KS_results$D[i] <- size_dist_resulsts[[i]]$statistic
 
  
  if(size_dist_resulsts[[i]]$p.value < 0.000161) { # post Bonferoni correction alpha value (0.05/ (28 + 3))
   sig[i] <- paste(size_dist_resulsts[[i]]$names)
   KS_results$sig[i] <- TRUE
   print("Found one!")
  }
    
}
 KS_results <- as.list(KS_results)
state_size <- ks.test(single_disturbence[single_disturbence$state == "OR",]$sizw, single_disturbence[single_disturbence$state == "FL",]$sizw )
KS_results$combination[length(names(dist_size))^2 +1] <- "Oregon x Florida"
KS_results$pval[length(names(dist_size))^2 +1] <- state_size$p.value
KS_results$sig[length(names(dist_size))^2 +1] <-  state_size$p.value < 0.000161
KS_results$D[length(names(dist_size))^2 +1] <- state_size$statistic

fl_8_3_8_5 <- ks.test(single_disturbence[single_disturbence$eco_II == "8.5",]$sizw, single_disturbence[single_disturbence$eco_II == "8.3",]$sizw )
or_6_2_7_1 <- ks.test(single_disturbence[single_disturbence$eco_II == "6.2",]$sizw, single_disturbence[single_disturbence$eco_II == "7.1",]$sizw )

KS_results$combination[length(names(dist_size))^2 +2] <- paste("8.5 x 8.3")
KS_results$pval[length(names(dist_size))^2 +2] <- fl_8_3_8_5$p.value
KS_results$sig[length(names(dist_size))^2 +2] <-  fl_8_3_8_5$p.value < 0.000161
KS_results$D[length(names(dist_size))^2 +2] <- fl_8_3_8_5$statistic

KS_results$combination[length(names(dist_size))^2 +3] <- paste("6.2 x 7.1")
KS_results$pval[length(names(dist_size))^2 +3] <- or_6_2_7_1$p.value
KS_results$sig[length(names(dist_size))^2 +3] <-  or_6_2_7_1$p.value < 0.000161
KS_results$D[length(names(dist_size))^2 +3] <- or_6_2_7_1$statistic


KS_results <- as.data.frame(KS_results)
KS_results <- KS_results[KS_results$pval != 1, ]

### Make table with results 
options(knitr.table.format = "html")

KS_results[,c(1:2, 4)] %>%
 # select(combination, pval, D) %>%
 kable(  booktabs = T, escape = F, digits = 5, row.names = FALSE, col.names = c("Comparison", "P value", "D statistic")) %>%
  kable_styling(latex_options = "striped", full_width = F) %>%
  #select(KS_results$sig == TRUE) %>%
  row_spec(which(KS_results$sig), bold = T, background = "#ADD8E6")# %>%
  
#write.csv2(KS_results, row.names = FALSE, file = "")


```

# Plotting Disturbence-level Abundance

This figure didn't make it into the paper, but is another _non MLE_ visualization tool. 

```{r}
## Making the upper and lower bounds
length <- length(single_disturbence[null_model_conditional,]$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence[null_model_conditional,]$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)

 
### Disturbances hex only

 single_disturbence[null_model_conditional, ] %>%
ggplot(aes(sizw, ratio, color = dist_name), show.legend = FALSE) +
  geom_hex() + 
  geom_line(aes(x =seq   , y = (upper )), color = "black")+
  geom_line(aes(x =seq  , y = (lower )), color = "black")+
scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log", breaks = c(1,10,100, 500),  low = "#636363", high = "#bdbdbd") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      #axis.title.y = element_blank(),
      #axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      legend.title = element_blank()
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("All Disturbances") + 
  scale_color_manual(values= disturbence_colors)+
  xlab("Area ha") +
  ylab("Interior / Total Ratio ")+ 
  ggtitle("Disturbance Types")+
  theme(panel.background = element_blank())
 
```


# Disturbence curves
 
```{r, echo=TRUE, message=FALSE, warning=FALSE}
### Disturbance Model lines
length <- length(single_disturbence[null_model_conditional,]$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence[null_model_conditional,]$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)

 single_disturbence[null_model_conditional, ] %>%
ggplot(aes(sizw, ratio), show.legend = TRUE) +
  geom_hex(aes(sizw, ratio)) + 
  geom_line(aes(x =seq   , y = (upper )), color = "black")+
  geom_line(aes(x =seq  , y = (lower )), color = "black")+
  geom_line(aes(x =seq, (mle_output$all_dist[[1]]$par[2]*seq^mle_output$all_dist[[1]]$par[3])/(mle_output$all_dist[[1]]$par[1] + seq^mle_output$all_dist[[1]]$par[3])), color = disturbence_colors[7])+ #5
   geom_line(aes(x =seq, (mle_output$all_dist[[2]]$par[2]*seq^mle_output$all_dist[[2]]$par[3])/(mle_output$all_dist[[2]]$par[1] + seq^mle_output$all_dist[[2]]$par[3])), color = disturbence_colors[5])+
   geom_line(aes(x =seq, (mle_output$all_dist[[3]]$par[2]*seq^mle_output$all_dist[[3]]$par[3])/(mle_output$all_dist[[3]]$par[1] + seq^mle_output$all_dist[[3]]$par[3]) ), color = disturbence_colors[4] )+
   geom_line(aes(x =seq, (mle_output$all_dist[[4]]$par[2]*seq^mle_output$all_dist[[4]]$par[3])/(mle_output$all_dist[[4]]$par[1] + seq^mle_output$all_dist[[4]]$par[3])), color = disturbence_colors[8])+
     geom_line(aes(x =seq, (mle_output$all_dist[[5]]$par[2]*seq^mle_output$all_dist[[5]]$par[3])/(mle_output$all_dist[[6]]$par[1] + seq^mle_output$all_dist[[5]]$par[3])), color = disturbence_colors[6])+
    geom_line(aes(x =seq, (mle_output$all_dist[[6]]$par[2]*seq^mle_output$all_dist[[6]]$par[3])/(mle_output$all_dist[[6]]$par[1] + seq^mle_output$all_dist[[6]]$par[3])), color = disturbence_colors[3])+
     geom_line(aes(x =seq, (mle_output$all_dist[[7]]$par[2]*seq^mle_output$all_dist[[7]]$par[3])/(mle_output$all_dist[[7]]$par[1] + seq^mle_output$all_dist[[7]]$par[3])), color = disturbence_colors[2])+
     geom_line(aes(x =seq, (mle_output$all_dist[[8]]$par[2]*seq^mle_output$all_dist[[8]]$par[3])/(mle_output$all_dist[[8]]$par[1] + seq^mle_output$all_dist[[8]]$par[3])),color = disturbence_colors[1] )+
    geom_line(aes(x =seq, (mle_output$all_dist[[9]]$par[2]*seq^mle_output$all_dist[[9]]$par[3])/(mle_output$all_dist[[9]]$par[1] + seq^mle_output$all_dist[[9]]$par[3])), color = disturbence_colors[9])+
scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log", breaks = c(1,10,100, 500),  low = "#636363", high = "#bdbdbd") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      #axis.title.y = element_blank(),
      #axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      #legend.position= "none"
      legend.title = element_blank()
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size (ha)") + 
  scale_color_manual(values= disturbence_colors)+
  xlab("Area ha") +
  ylab("Interior / Total Ratio ")+ 
  ggtitle("All Disturbances")+
  theme(panel.background = element_blank())
```


# State Within Disturbence

```{r, echo=TRUE, message=FALSE, warning=FALSE}

 ### Disturbance by state FL
length <- length(single_disturbence[null_model_conditional & single_disturbence$state == "FL",]$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence[null_model_conditional,]$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)
 single_disturbence[null_model_conditional & single_disturbence$state == "FL", ] %>%
ggplot(aes(sizw, ratio), show.legend = FALSE) +
  geom_hex() + 
  geom_line(aes(x =seq   , y = (upper )), color = "black")+
  geom_line(aes(x =seq  , y = (lower )), color = "black")+
  geom_line(aes(x =seq, (mle_output$all_dist_fl[[1]]$par[2]*seq^mle_output$all_dist_fl[[1]]$par[3])/(mle_output$all_dist_fl[[1]]$par[1] + seq^mle_output$all_dist_fl[[1]]$par[3]) ), color = disturbence_colors[7])+ #5
   geom_line(aes(x =seq, (mle_output$all_dist_fl[[2]]$par[2]*seq^mle_output$all_dist_fl[[2]]$par[3])/(mle_output$all_dist_fl[[2]]$par[1] + seq^mle_output$all_dist_fl[[2]]$par[3]) ), color = disturbence_colors[5])+
   geom_line(aes(x =seq, (mle_output$all_dist_fl[[3]]$par[2]*seq^mle_output$all_dist_fl[[3]]$par[3])/(mle_output$all_dist_fl[[3]]$par[1] + seq^mle_output$all_dist_fl[[3]]$par[3]) ), color = disturbence_colors[4] )+
   geom_line(aes(x =seq, (mle_output$all_dist_fl[[4]]$par[2]*seq^mle_output$all_dist_fl[[4]]$par[3])/(mle_output$all_dist_fl[[4]]$par[1] + seq^mle_output$all_dist_fl[[4]]$par[3]) ), color = disturbence_colors[8])+
     geom_line(aes(x =seq, (mle_output$all_dist_fl[[5]]$par[2]*seq^mle_output$all_dist_fl[[5]]$par[3])/(mle_output$all_dist_fl[[6]]$par[1] + seq^mle_output$all_dist_fl[[5]]$par[3])  ), color = disturbence_colors[6])+
    geom_line(aes(x =seq, (mle_output$all_dist_fl[[6]]$par[2]*seq^mle_output$all_dist_fl[[6]]$par[3])/(mle_output$all_dist_fl[[6]]$par[1] + seq^mle_output$all_dist_fl[[6]]$par[3])), color = disturbence_colors[3])+
     geom_line(aes(x =seq, (mle_output$all_dist_fl[[7]]$par[2]*seq^mle_output$all_dist_fl[[7]]$par[3])/(mle_output$all_dist_fl[[7]]$par[1] + seq^mle_output$all_dist_fl[[7]]$par[3])  ), color = disturbence_colors[2])+
     geom_line(aes(x =seq, (mle_output$all_dist_fl[[8]]$par[2]*seq^mle_output$all_dist_fl[[8]]$par[3])/(mle_output$all_dist_fl[[8]]$par[1] + seq^mle_output$all_dist_fl[[8]]$par[3]) ),color = disturbence_colors[1] )+
    geom_line(aes(x =seq, (mle_output$all_dist_fl[[9]]$par[2]*seq^mle_output$all_dist_fl[[9]]$par[3])/(mle_output$all_dist_fl[[9]]$par[1] + seq^mle_output$all_dist_fl[[9]]$par[3])    ), color = disturbence_colors[9])+
scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log", breaks = c(1,10,100, 500),  low = "#636363", high = "#bdbdbd") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      #axis.title.y = element_blank(),
      #axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      legend.position= "none"
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size (ha)") + 
  scale_color_manual(values= disturbence_colors)+
  xlab("Area ha") +
  ylab("Interior / Total Ratio ")+ 
  ggtitle("Florida")+
  theme(panel.background = element_blank())
  
 
 ### Disturbance by state OR
 length <- length(single_disturbence[null_model_conditional & single_disturbence$state == "OR",]$sizw)
length <- length + 1
seq <- c(2:length)
seq[length(seq)] <- max(single_disturbence[null_model_conditional,]$sizw)
lower <- lower_bound_ratios(seq)
upper <- upper_bound_ratios(seq)
 
 
  single_disturbence[null_model_conditional & single_disturbence$state == "OR", ] %>%
ggplot(aes(sizw, ratio), show.legend = TRUE) +
  geom_hex() + 
  geom_line(aes(x =seq   , y = (upper )), color = "black")+
  geom_line(aes(x =seq  , y = (lower )), color = "black")+
  geom_line(aes(x =seq, (mle_output$all_dist_or[[1]]$par[2]*seq^mle_output$all_dist_or[[1]]$par[3])/(mle_output$all_dist_or[[1]]$par[1] + seq^mle_output$all_dist_or[[1]]$par[3])   ), color = disturbence_colors[7])+ #5
   geom_line(aes(x =seq, (mle_output$all_dist_or[[2]]$par[2]*seq^mle_output$all_dist_or[[2]]$par[3])/(mle_output$all_dist_or[[2]]$par[1] + seq^mle_output$all_dist_or[[2]]$par[3])   ), color = disturbence_colors[5])+
   geom_line(aes(x =seq, (mle_output$all_dist_or[[3]]$par[2]*seq^mle_output$all_dist_or[[3]]$par[3])/(mle_output$all_dist_or[[3]]$par[1] + seq^mle_output$all_dist_or[[3]]$par[3])  ), color = disturbence_colors[4] )+
   geom_line(aes(x =seq, (mle_output$all_dist_or[[4]]$par[2]*seq^mle_output$all_dist_or[[4]]$par[3])/(mle_output$all_dist_or[[4]]$par[1] + seq^mle_output$all_dist_or[[4]]$par[3])  ), color = disturbence_colors[8])+
     geom_line(aes(x =seq, (mle_output$all_dist_or[[5]]$par[2]*seq^mle_output$all_dist_or[[5]]$par[3])/(mle_output$all_dist_or[[6]]$par[1] + seq^mle_output$all_dist_or[[5]]$par[3])    ), color = disturbence_colors[6])+
    geom_line(aes(x =seq, (mle_output$all_dist_or[[6]]$par[2]*seq^mle_output$all_dist_or[[6]]$par[3])/(mle_output$all_dist_or[[6]]$par[1] + seq^mle_output$all_dist_or[[6]]$par[3])  ), color = disturbence_colors[3])+
     geom_line(aes(x =seq, (mle_output$all_dist_or[[7]]$par[2]*seq^mle_output$all_dist_or[[7]]$par[3])/(mle_output$all_dist_or[[7]]$par[1] + seq^mle_output$all_dist_or[[7]]$par[3])   ), color = disturbence_colors[2])+
     geom_line(aes(x =seq, (mle_output$all_dist_or[[8]]$par[2]*seq^mle_output$all_dist_or[[8]]$par[3])/(mle_output$all_dist_or[[8]]$par[1] + seq^mle_output$all_dist_or[[8]]$par[3])   ),color = disturbence_colors[1] )+
    geom_line(aes(x =seq, (mle_output$all_dist_or[[9]]$par[2]*seq^mle_output$all_dist_or[[9]]$par[3])/(mle_output$all_dist_or[[9]]$par[1] + seq^mle_output$all_dist_or[[9]]$par[3])    ), color = disturbence_colors[9])+
scale_x_continuous(trans="log") +
scale_fill_gradient(trans = "log", breaks = c(1,10,100, 500),  low = "#636363", high = "#bdbdbd") +
   theme(panel.background = element_blank(),
      #axis.text.y = element_blank(),
      #axis.title.y = element_blank(),
      #axis.ticks.y = element_blank(),
      axis.text.x = element_text(size=14),
      axis.text.y = element_text(size=14), 
      #legend.position= "none"
      ) + 
scale_x_log10(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
  xlab("Disturbance Event Size (ha)") + 
  scale_color_manual(values= disturbence_colors)+
  xlab("Area ha") +
  ylab("Interior / Total Ratio ")+ 
  ggtitle("Oregon")+
  theme(panel.background = element_blank())
  
```





