---
title: "Simulate Disturbances"
author: "Dietze"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, fig.asp=1}
library(rlang)
library(raster)
### gap disturbance
nrow = 5#1000  ## 1000 takes ~60 sec
ncol = nrow
ntime = 5 #1000
ages = matrix(0,nrow,ncol)
p.init= 0.01

## run simulation
gfile = "ages.gap.RData"
if(file.exists(gfile)){
  load(gfile)
  ages = ages.gap
  sorted = sorted.gap
} else {
  start = proc.time()
  ages = gap_disturb_raster(ages,p.init,ntime)
  proc.time()-start
}

# Map
image(log10(ages),xlab="",ylab="",xaxt="n",yaxt="n",asp=1)

## age distribution
par(mar=c(5,5,4,2))
nt=300
time = 0:nt
hist(ages+0.001,probability = TRUE,xlim=c(0,nt),breaks=nt,xlab="Age (years)",main="Gap Dynamics",cex.main=1.75,cex.lab=1.75,cex.axis=1.5) #breaks=0:(max(ages)+1)
lines(time,dgeom(time,p.init),col=3,lwd=3,type='s')

## aggregate age classes
n = 10
dn = 10
ac <- floor(ages/dn)
ac[ac>n] <- n
hist(ac)

## calculate adjacency matrix
if(!file.exists(gfile)){
  start = proc.time()
  r <- raster::raster(ncol=ncol, nrow=ncol)
  raster::values(r) <- ac #ages
  #foo <- get_ratio_basic(r,"test")  ## returns adj(size) by disturbance; can also use to construct size distribution
  test <- raster_to_age_matrix(r)
  proc.time()-start  ## took ~2 min at 1000x and 10 classes
  
  ## sort adjacency matrix
ord <- order(as.numeric(rownames(test)))
br <- test[ord,] ## sort by row
sorted <- br[,ord] ## sorted adjacency matrix
sorted <- sorted[,!is.na(colnames(sorted))]
sorted <- sorted[!is.na(rownames(sorted)),]
  
}

## display matrix
## initial version is transposed
# image(1:nrow(sorted), 1:ncol(sorted), log(sorted[,ncol(sorted):1]),col=terrain.colors(30), 
#       axes = FALSE,xlab="Age Class",ylab="Age Class",cex.lab=1.8)
# axis(3, 1:nrow(sorted), colnames(sorted)) ## top label
# axis(2, ncol(sorted):1, rownames(sorted))
# for (y in 1:ncol(sorted))
#   for (x in 1:nrow(sorted))
#     text(x, ncol(sorted)-y+1, format(sorted[x,y],digits=2),cex=2)
par(mar=c(2,5,7,2))
image(1:nrow(sorted), 1:ncol(sorted), log(t(sorted[ncol(sorted):1,])),col=terrain.colors(30), 
      axes = FALSE,ylab="Age Class",main="Age Class",cex.lab=1.8,xlab=" ",cex.main=1.8,font.lab=2)
axis(3, 1:nrow(sorted), colnames(sorted),cex.axis=1.5) ## top label
axis(2, ncol(sorted):1, rownames(sorted),cex.axis=1.5)
for (y in 1:ncol(sorted))
  for (x in 1:nrow(sorted))
    text(x, ncol(sorted)-y+1, format(sorted[y,x],digits=2),cex=2)


## if needed, aggregate the matrix
## this code was developed when age wasn't aggregated first
if(FALSE){
  colage <- as.numeric(colnames(sorted))
  colage <- ceiling(colage/dn)
  colage[colage>n] <- n
  br <- t(apply(sorted,1,tapply,colage,sum))
  aggAdj <- apply(br,2,tapply,colage,sum)
  aggAdj  ## aggregated adjacency matrix
}

#save simulations for later
ages.gap = ages
sorted.gap = sorted
save(ages.gap,sorted.gap,file=gfile)
```


## Simulate contagious disturbance
```{r, fig.asp=1}
### contagious disturbance
nrow =  100#1000
ncol = nrow
years = 100 #1000 #1000
ages = matrix(0,nrow,ncol)
p.init=  0.01
ps = 0.25

## simulation
#sfile = "ages.spread.RData"
if(file.exists(sfile)){
  load(sfile)
} else {
  start = proc.time()
  ages.spread = contagion_disturb_raster(ages,p.init,ps,years)
  save(ages.spread,file=sfile)
  proc.time()-start ## 1000x landscape for 1000 timesteps took ~1.5hr
}

## full image
#image(1:nrow,1:ncol, log10(ages.spread),xlab="",ylab="",asp=1)
#rect(800,800,900,900,col=NA,lwd=2)

## inset image
image(800:900,800:900,log10(ages.spread[800:900,800:900]),xlab="",ylab="",asp=1)

## age distribution
par(mar=c(5,5,4,2))
nt=100
time = 0:nt
hist(ages.spread+0.0001,probability = TRUE,xlim=c(0,nt),breaks=99,xlab="Age (years)",main="Contagious Spread",cex.main=1.75,cex.lab=1.75,cex.axis=1.5)
#lines(time,dgeom(time,1/mean(ages.spread)),col=3,lwd=3,type='s')
lines(time,dgeom(time,p.init/ps),col=3,lwd=3,type='s')

## rate
1/mean(ages.spread) ## emergent
(1/mean(ages.spread))/p.init ## normed by initation
## would be good to figure out the math on this -- seems like it should be NB(4,ps)
## which has an expected value of ps*4/(1-ps), but that ends up being too small
## because it fails to account that each successful spread then has 3 neighboors


## aggregate age classes
n = 10
dn = 10
asc <- floor(ages.spread/dn)
asc[asc>n] <- n
hist(asc)

## calculate adjacency matrix
safile = "adj.spread.RData"
if(file.exists(safile)){
  load(safile)
} else {
  start = proc.time()
  r <- raster::raster(ncol=ncol, nrow=ncol)
  raster::values(r) <- asc #ages
  test <- raster_to_age_matrix(r)
  save(test,file=safile)
  proc.time()-start  ## took 21 sec at 1000x and 10 classes
}

## sort adjacency matrix
ord <- order(as.numeric(rownames(test)))
br <- test[ord,] ## sort by row
sorted <- br[,ord] ## sorted adjacency matrix
sorted <- sorted[,!is.na(colnames(sorted))]
sorted <- sorted[!is.na(rownames(sorted)),]

## display matrix
image(1:nrow(sorted), 1:ncol(sorted), log(sorted[,ncol(sorted):1]),col=terrain.colors(30), 
      axes = FALSE,xlab="Age Class",ylab="Age Class",cex.lab=1.8)
axis(3, 1:nrow(sorted), colnames(sorted)) ## top label
axis(2, ncol(sorted):1, rownames(sorted))
for (y in 1:ncol(sorted))
  for (x in 1:nrow(sorted)){
    a = sorted[x,y]
    a = ifelse(a > 0.01,format(a,digits=2), format(a,digits=1,scientific = TRUE))
    text(x, ncol(sorted)-y+1, a,cex=1)
  }

## matrix transposed
par(mar=c(2,5,7,2))
image(1:nrow(sorted), 1:ncol(sorted), log(t(sorted[ncol(sorted):1,])),col=terrain.colors(30), 
      axes = FALSE,ylab="Age Class",main="Age Class",cex.lab=1.8,xlab=" ",cex.main=1.8,font.lab=2)
axis(3, 1:nrow(sorted), colnames(sorted),cex.axis=1.5) ## top label
axis(2, ncol(sorted):1, rownames(sorted),cex.axis=1.5)
for (y in 1:ncol(sorted))
  for (x in 1:nrow(sorted))
    text(x, ncol(sorted)-y+1, format(sorted[y,x],digits=2),cex=2)

## diagonal decay
plot(0:n,diag(sorted),ylim=c(0,sorted[1,1]))
rate = diag(sorted)
rate = mean((rate[-1]/rate[-(n+1)])[-n])
decay = sorted[1,1]*rate^(0:n)
decay[n+1] = decay[n+1]+ sorted[1,1]*sum(rate^((n+1):1000))/sum(rate^(0:1000))  ## last class should be tail cumulative
lines(0:n,decay)
lines(0:n,sorted[1,],col=2)
lines(0:n,sorted[4,],col=3)
lines(0:n,sorted[9,],col=4)


# verifying that rows sum to 1
apply(sorted,1,sum)


```

Do we get the size distribution of disturbances correct
```{r, fig.asp=1}

newD <- ceiling(ages.spread/years) ## split map into binary 0 = this year's disturbance, 1 = older
image(newD)

## calculate disturbance sizes
ndfile = "newD.RData"
if(file.exists(ndfile)){
  load(ndfile)
} else {
  start = proc.time()
  r <- raster::raster(ncol=ncol, nrow=ncol)
  raster::values(r) <- 1-newD
  foo <- get_ratio_basic(r,"test")  ## returns adj(size) by disturbance; can also use to construct size distribution
  proc.time()-start
  save(foo,file=ndfile)
}

## simulated size distribution
sz <- graphics::hist(foo$size,probability=TRUE,main="Disturbance size distribution",breaks=1:max(foo$size))

## simulated cumulative disturbance distribution
nz <- length(sz$breaks)
plot(sz$breaks[-nz],cumsum(sz$breaks[-nz]*sz$counts)*100/(nrow*ncol),type='s',xlab="Disturbance size (pixels)",ylab="Cumulative Area Disturbed (%)")

## Analytical disturbance approximation
A = sorted
I = matrix(0,n+1,nz)
PS = 1-dbinom(0,4,ps)
PS = 0.705
f.area = table(asc)/(nrow*ncol)
I[,1] = p.init * f.area ## this should be multiplied by initial fractional areas
for(k in 2:nz){
  I[,k] = I[,k-1]%*%(PS*A)
}
#plot(1:nz,apply(I,2,sum))
#lines(sz$mids,sz$density)

## cumulative
Ai = apply(I,2,sum)
Aid = c(-diff(Ai),Ai[length(Ai)])
Aid = Aid * (1:nz)
#plot(cumsum(Aid))

plot(sz$breaks[-nz],cumsum(sz$breaks[-nz]*sz$counts)*100/(nrow*ncol),type='s',xlab="Disturbance size (pixels)",ylab="Cumulative Area Disturbed (%)")
lines(1:nz,cumsum(Aid)*100,type='s',col=2)

## simulated curve accumulates too fast
## am I missing something to do with multiple trials at each size
## or is it something to do with random disturbances aggregating geometrically?

D = sz$breaks[-nz]*sz$counts/(nrow*ncol)
D[2:(nz)]/D[1:(nz-1)]


```



Starting from a disturbance map, run the simulation forward one time step (multiple times) for a special case (e.g. initiation only occurring in a specific age class) to see if spatial adjacency approximation can correctly capture the area disturbed and the cumulative size distribution.

```{r}
age0 = ages
```


```{r}
## generate a few more disturbance realizations
adj.dist <- list()
ad.hist <- list()

## simulation
j = 1
sfile = paste0("spread.",j,".RData")
if(file.exists(sfile)){
  load(sfile)
} else {
  start = proc.time()
  spread = contagion_disturb_raster(matrix(0,nrow,ncol),p.init,ps,1)
  r <- raster::raster(ncol=ncol, nrow=nrow)
  raster::values(r) <- 1-spread
  adj.dist[[j]] <- get_ratio_basic(r,"test")  ## returns adj(size) by disturbance; can also use to construct size distribution
  proc.time()-start
  save(adj.dist,file=sfile)
}
  
ad.hist[[j]] <- graphics::hist(adj.dist[[j]]$size,probability=TRUE,main="Disturbance size distribution",breaks=1:max(adj.dist[[j]]$size))

## simulated cumulative disturbance distribution
nzj <- length(ad.hist[[j]]$breaks)
plot(sz$breaks[-nz],cumsum(sz$breaks[-nz]*sz$counts)*100/(nrow*ncol),
type='s',xlab="Disturbance size (pixels)",ylab="Cumulative Area Disturbed (%)")
lines(ad.hist[[j]]$breaks[-nzj],cumsum(ad.hist[[j]]$breaks[-nzj]*ad.hist[[j]]$counts)*100/(nrow*ncol),col="grey",type="s")
      
```

```{r}
if(FALSE){
## Can the model be calibrated to get total area correct?
Ps <- seq(0,0.3,by=0.025)
np <- length(Ps)
area_sim <- area_calc <- area_calcbin <- rep(NA,np)
for(i in seq_along(Ps)){
  print(paste(i,"of",np,": ",Ps[i]))
  
  ## simulated map
  area_sim[i] <- sum(1-contagion_disturb_raster(matrix(0,nrow,ncol),p.init,Ps[i],1))

  ## run analytical approximation
  I = Ib = rep(0,100)
  PS = 1-dbinom(0,4,Ps[i])
  I[1] = Ib[1] = p.init ## this should be multiplied by initial fractional areas
  for(k in 2:nz){
    I[k] = I[k-1]*Ps[i]
    Ib[k] = Ib[k-1]*PS
  }
  area_calc[i] <- sum(I)
  area_calcbin[i] <- sum(Ib)
}

}
plot(Ps,area_sim/(nrow*ncol),log='y',type='b',lwd=2,cex.lab=1.5,
     xlim=c(0,0.3),xlab="Spread probability",ylab="Fraction of landscape disturbed")
#lines(Ps,area_calc,col=2)
lines(Ps,area_calcbin,col=3,lwd=2)
legend("topleft",lwd=2,col=c(1,3),legend=c("Simulation","Analytical"),cex=1.2)

### also, for a heterogeneous map, do we get the _relative_ fractional areas right?
```

**Forward simulation of adjacency and fractional area**
```{r}
nt = 1000 ## number of time steps
na = 100 ## number of age classes for forward simulation
nk = 100 ## number of steps to model spread (max disturbance size)
p.init = 0.01
ps = 0.10
Ps = 1-dbinom(0,4,ps)
A = array(0,c(na,na,nt))  ## adjacency matrix (through time)
f = matrix(0,na,nt)  ## fractional area vector (through time)
## initialize at age 0
## note indexing in code is one off from paper because R doesn't like zero indexing
A[1,1,1] = 1 
f[1,1] = 1

## calculate adjacency look up
ndfile = "newD.RData"
load(ndfile)
adj.raw <- tapply(foo$ratio,foo$size,mean)
adj <- rep(NA,nk)
adj[as.numeric(names(adj.raw))] <- adj.raw
adj.approx <- approx(as.numeric(names(adj.raw)),adj.raw,xout = 1:nk)
isna <- which(is.na(adj))
adj[isna] <- adj.approx$y[isna]
adj[which(is.na(adj))] <- max(adj,na.rm = TRUE)
plot(adj,type='l')
points(as.numeric(names(adj.raw)),adj.raw,col=2)


for(t in 1:(nt-1)){
  
  ## calculate disturbance
  I <- matrix(0,nk,na)  ## storage of ignition
  I[1,] <- p.init*f[,t] ## disturbance initiation
  for(k in 1:(nk-1)){
    I[k+1,] = I[k,]%*%(Ps*A[,,t])
  }
  D <- apply(I,2,sum)
  
  ## update fractional areas
  f[1,t+1] <- sum(D) ## newly disturbed area is the sum of disturbances by age class
  for(k in 2:na){
    f[k,t+1] <- max(f[k-1,t]-D[k-1],0)
  }
  f[na,t+1] <- max(f[na,t+1] + f[na,t] - D[na],0) ## end case: merge
  
  ## calculate disturbance size distribution (todo: by age class)
  Ai = apply(I,1,sum)
  Aid = c(-diff(Ai),Ai[nk])
  Aid = Aid * (1:nk)
  if(FALSE){
     plot(Aid)
     plot(cumsum(Aid))
  }
  
  ## update A00
  sps <- (1:nk)*Aid
  num <- (adj+f[1,t+1]*(1-adj))*sps
  A00 <- sum(num)/sum(sps)
  A[1,1,t+1] <- A00
  
  ## update disturbed adjacent to non-disturbed
  for(k in 2:na){
    A[1,k,t+1] <- D[k-1]/sum(D)*(1-A00)  ## it's possibly this should be a weighted average (by f_area)
  }
  A[1,na,t+1] <- A[1,na,t+1] + D[na]/sum(D)*(1-A00)
  
  ## update non-disturbed adjacent to non-disturbed
  for(j in 2:na){
    for(k in 2:na){
      A[j,k,t+1] <- ifelse(f[j-1,t]>0,A[j-1,k-1,t]*(1-D[j-1]/f[j-1,t]),0) ## D/f is a hack that's not in the derivation
    }
    A[j,na,t+1] <- A[j,na,t+1] + ifelse(f[na,t]>0,A[j-1,na,t]*(1-D[na]/f[na,t]),0) ## sum by row
  }
  A[na,,t+1] <- (A[na,,t+1] + A[na,,t]*ifelse(f[na,t]>0,(1-D[na]/f[na,t]),0))/2 ## average by col  *** should be a weighted average by fractional area
  
  ## update non-disturbed adjacent to disturbed
  for(j in 2:na){
    #A[j,1,t+1] <- D[j-1]/f[j-1,t]#1 - sum(A[j,,t+1])
    A[j,1,t+1] <- ifelse(f[j,t+1]>0,max(0,1 - sum(A[j,,t+1])),0)
  }
#  A[j,1,t+1] <- A[j,1,t+1] + D[na]#/f[na,t]
  
  if(t%%100 == 0) print(t)
}

image(1:na, 1:na, log(A[,na:1,t+1]),col=terrain.colors(30), 
      axes = FALSE,xlab="Age Class",ylab="Age Class",cex.lab=1.8)

## aggregate to decade
  colage <- ceiling(1:na/dn)
  colage[colage>n] <- n
  br <- t(apply(A[,,t],1,tapply,colage,sum))
  aggAdj <- apply(br,2,tapply,colage,mean)
  aggAdj  ## aggregated adjacency matrix

## display matrix
image(1:n, 1:n, log(aggAdj[,n:1]),col=terrain.colors(30), 
      axes = FALSE,xlab="Age Class",ylab="Age Class",cex.lab=1.8)
axis(3, 1:n, 1:n) ## top label
axis(2, n:1, 1:n)
for (y in 1:n)
  for (x in 1:n){
    a = aggAdj[x,y]
    a = ifelse(a > 0.01,format(a,digits=2), format(a,digits=1,scientific = TRUE))
    text(x, n-y+1, a,cex=1)
  }
  
```


## Compare math of adj to simulation
```{r, fig.asp=1}
### contagious disturbance
nrow = 1000
ncol = nrow
years = 1000

## simulation
s10file = "ages.spread10.RData"
if(file.exists(s10file)){
  load(s10file)
} else {
  start = proc.time()
  ages.spread10 = contagion_disturb_raster(matrix(0,nrow,ncol),p.init,ps,years)
  save(ages.spread10,file=s10file)
  proc.time()-start ## 1000x landscape for 1000 timesteps took ~1.5hr
}

## full image
#image(1:nrow,1:ncol, log10(ages.spread10),xlab="",ylab="",asp=1)
#rect(800,800,900,900,col=NA,lwd=2)

## inset image
image(800:900,800:900,log10(ages.spread10[800:900,800:900]),xlab="",ylab="",asp=1)

## age distribution
nt=100
time = 0:nt
hist(ages.spread10+0.0001,probability = TRUE,xlim=c(0,nt),breaks=0:years,xlab="Age (years)",main="Contagious Spread")
lines(time,dgeom(time,1/mean(ages.spread10)),col=3,lwd=3,type='s')
#lines(time,dgeom(time,p.init/ps),col=3,lwd=3,type='s')

## rate
1/mean(ages.spread10) ## emergent
(1/mean(ages.spread10))/p.init ## normed by initation
## would be good to figure out the math on this -- seems like it should be NB(4,ps)
## which has an expected value of ps*4/(1-ps), but that ends up being too small
## because it fails to account that each successful spread then has 3 neighboors


## aggregate age classes
n = 10
dn = 10
asc <- floor(ages.spread10/dn)
asc[asc>n] <- n
hist(asc)

## calculate adjacency matrix
sa10file = "adj.spread10.RData"
if(file.exists(sa10file)){
  load(sa10file)
} else {
  start = proc.time()
  r <- raster::raster(ncol=ncol, nrow=ncol)
  raster::values(r) <- asc #ages
  test10 <- raster_to_age_matrix(r)
  save(test10,file=sa10file)
  proc.time()-start  ## took 21 sec at 1000x and 10 classes
}

## sort adjacency matrix
ord <- order(as.numeric(rownames(test10)))
br <- test10[ord,] ## sort by row
sort10 <- br[,ord] ## sorted adjacency matrix
sort10 <- sort10[,!is.na(colnames(sort10))]
sort10 <- sort10[!is.na(rownames(sort10)),]

## display matrix
image(1:nrow(sort10), 1:ncol(sort10), log(sort10[,ncol(sort10):1]),col=terrain.colors(30), 
      axes = FALSE,xlab="Age Class",ylab="Age Class",cex.lab=1.8)
axis(3, 1:nrow(sort10), colnames(sort10)) ## top label
axis(2, ncol(sort10):1, rownames(sort10))
for (y in 1:ncol(sort10))
  for (x in 1:nrow(sort10)){
    a = sort10[x,y]
    a = ifelse(a > 0.01,format(a,digits=2), format(a,digits=1,scientific = TRUE))
    text(x, ncol(sort10)-y+1, a,cex=1)
  }
##transposed
par(mar=c(2,5,7,2))
image(1:nrow(sort10), 1:ncol(sort10), log(t(sort10[ncol(sort10):1,])),col=terrain.colors(30), 
      axes = FALSE,ylab="Age Class",main="Age Class",cex.lab=1.8,xlab=" ",cex.main=1.8,font.lab=2)
axis(3, 1:nrow(sort10), colnames(sort10),cex.axis=1.5) ## top label
axis(2, ncol(sort10):1, rownames(sort10),cex.axis=1.5)
for (y in 1:ncol(sort10))
  for (x in 1:nrow(sort10))
    text(x, ncol(sort10)-y+1, format(sort10[y,x],digits=2),cex=2)



## display analytical matrix
image(1:nrow(aggAdj), 1:ncol(aggAdj), log(aggAdj[,ncol(aggAdj):1]),col=terrain.colors(30), 
      axes = FALSE,xlab="Age Class",ylab="Age Class",cex.lab=1.8)
axis(3, 1:nrow(aggAdj), colnames(aggAdj)) ## top label
axis(2, ncol(aggAdj):1, rownames(aggAdj))
for (y in 1:ncol(aggAdj))
  for (x in 1:nrow(aggAdj)){
    a = aggAdj[x,y]
    a = ifelse(a > 0.01,format(a,digits=2), format(a,digits=1,scientific = TRUE))
    text(x, ncol(aggAdj)-y+1, a,cex=1)
  }

## analytical transposed
par(mar=c(2,5,7,2))
image(1:nrow(aggAdj), 1:ncol(aggAdj), log(t(aggAdj[ncol(aggAdj):1,])),col=terrain.colors(30), 
      axes = FALSE,ylab="Age Class",main="Age Class",cex.lab=1.8,xlab=" ",cex.main=1.8,font.lab=2)
axis(3, 1:nrow(aggAdj), colnames(aggAdj),cex.axis=1.5) ## top label
axis(2, ncol(aggAdj):1, rownames(aggAdj),cex.axis=1.5)
for (y in 1:ncol(aggAdj))
  for (x in 1:nrow(aggAdj))
    text(x, ncol(aggAdj)-y+1, format(aggAdj[y,x],digits=2),cex=2)

## diagonal decay
plot(0:n,diag(sort10),ylim=c(0,sort10[1,1]))
rate = diag(sort10)
rate = mean((rate[-1]/rate[-(n+1)])[-n])
decay = sort10[1,1]*rate^(0:n)
decay[n+1] = decay[n+1]+ sort10[1,1]*sum(rate^((n+1):1000))/sum(rate^(0:1000))  ## last class should be tail cumulative
lines(0:n,decay)
lines(0:n,sort10[1,],col=2)
lines(0:n,sort10[4,],col=3)
lines(0:n,sort10[9,],col=4)


# verifying that rows sum to 1
apply(sort10,1,sum)

```


Sorting through spread probability
```{r}

## prob of spreading 1 or more = 1-prob not spreading
## --------------------------------------------------
Ps1 = 1-dbinom(0,4,ps) # = 1-pbinom(0,4,ps)


## probability of spreading 2 or more | 1
## --------------------------------------------------

# from the original cell with adj A
Ps2.1 = 1-pbinom(1,4,ps) # = dbinom(2,4,ps)+dbinom(3,4,ps)+dbinom(4,4,ps)

# from the second cell with adj A^2
Ps2.2 = 1-pbinom(0,3,ps)

# how are these two combined? does the second need to be downweighted by ps?
Ps2.1 + Ps2.2

## probability of spreading 3 or more | 2
## --------------------------------------------------

# from the original cell with A
Ps3.1 = 1-pbinom(2,4,ps)

# from an A^2 cell
Ps3.2 = 2*(1-pbinom(0,3,ps)) + (1-pbinom(1,3,ps))

# from an A^3 cell
Ps3.3 = 1-pbinom(0,3,ps)

Ps3.1 + Ps3.2 + Ps3.3

## probability of spreading 4 or more | 3

Ps4.1 = 1-pbinom(3,4,ps)

Ps4.2 = ... etc

## what are all the ways of achieving an A^1 spread?
Ps1 + Ps2.1 + Ps3.1 + Ps4.1

## what are all the ways of achieving A^2 spread?
Ps2.2 + Ps3.2 + Ps4.2 + ... + Ps8.2
## 4 outwardly expanding cases
## 8 cases where a cell has 2 possible paths

```

